draft 1

### 2016-05-26 finalwriteup/draft.rmd
trying to fix

Structure:

>>>>

#### Initial Trial of five Methods

To begin analysis, all prediction methods were trialled using as much data as possible for each method. Boosted trees and Naiive bayes algorithm are able to process data with missing values, so all data could be used. Logistic regression, randomForest and Bayesian Networks require complete datasets so a subset of complete data was used for these. It was expected that Boosted trees would perform best as they are powerful and can use incomplete data. For this reason, 4 x 5 fold runs of each method were performed (20 models total for each method) and statistically compared against boosted trees. A power calculation was used to calculate the number of runs required for a statistical power of 0.8.

The models were compared using the Area under the curve (AUC) test statistic calculated from the Reciever Operating Curve (ROC) as this gives a good indication of model performance under binary classification [@pROC][@Putler2012]. An example plot of five ROC's resulting from five fold cross validation models using the boosted tree algorithm is shown below:

```{r}
# image below generated from file rf_log_naiive_auc.rmd
# lines 683 to 689

![](images/boosted tree/5_fold_ROC.png)

[@pROC]

* Boosted trees first tuned using caret package [@caret]:
* shrinkage = 0.001
* no trees = 10000
* min terminal node size = 20
* max tree depth = 5
